network_analysis

### 2020-07-16 analyses/network_analysis.Rmd
woohoo SEM!

### Prepare environment
```{r setup, include=FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(tidyverse)
library(lubridate)
```

@@

@@

### Now let's try all this with GLMMs
```{r}
##### niche overlap
lmer_niche.overlap <- lmer(niche.overlap.HL ~ elev.mean + 
                            I(elev.mean^2) +
                            I(elev.mean^3) +
                            bb.rich +
                            fl.rich +
                            log.fl.abund +
                            bb.abund +
                            (1 | year),
                          data = netmet)

step(lmer_niche.overlap,reduce.random=FALSE) # stepwise variable selection; commented-out variables were removed based on the results of this step
summary(glm_niche.overlap)

#####  c-score
lmer_c.score <- lmer(C.score.HL ~ elev.mean + 
                            I(elev.mean^2) +
                            I(elev.mean^3) +
                            bb.rich +
                            fl.rich +
                            log.fl.abund +
                            bb.abund +
                            (1 | year),
                          data = netmet)

step(lmer_c.score,reduce.random=FALSE) # stepwise variable selection; commented-out variables were removed based on the results of this step
summary(lmer_c.score)

```

@@

### Since we clearly have structured collinearity in our preditors, i.e. elevation shapes abundance and diversity which shape network structure, perhaps SEM could be appropriate? The main question is whether it can handle the potentially complex (nonlinear) relationships between elevation and diversity/abundance, and whether it can handle the hierarchical structure of my data.
```{r}
library(lavaan)

```

>>>>

### Prepare environment
```{r setup, include=FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(lavaan)
library(tidyverse)
library(lubridate)
```

@@

### Since we clearly have structured collinearity in our preditors, i.e. elevation shapes abundance and diversity which shape network structure, perhaps SEM could be appropriate? The main question is whether it can handle the potentially complex (nonlinear) relationships between elevation and diversity/abundance, and whether it can handle the hierarchical structure of my data.
```{r}
library(piecewiseSEM)

netmet.scaled <- netmet %>%
  select(site, year, niche.overlap.HL, elev.mean, fl.rich, bb.rich, log.fl.abund, log.bb.abund) %>%
  mutate(niche.overlap.HL = scale(niche.overlap.HL),
         elev.mean = scale(elev.mean),
         fl.rich = scale(fl.rich),
         log.fl.abund = scale(log.fl.abund),
         log.bb.abund = scale(log.bb.abund)) %>%
  as.matrix() %>%
  as_tibble() %>%
  mutate(niche.overlap.HL = as.numeric(niche.overlap.HL),
         elev.mean = as.numeric(elev.mean),
         fl.rich = as.numeric(fl.rich),
         log.fl.abund = as.numeric(log.fl.abund),
         log.bb.abund = as.numeric(log.bb.abund),
         site = factor(site),
         year = factor(year)) %>%
  na.omit()

mod_niche.overlap <- psem(lmer(niche.overlap.HL ~ elev.mean + 
                                fl.rich + log.bb.abund + 
                                 (1 | year) + (1 | site), 
                              netmet.scaled),
                          lm(fl.rich ~ elev.mean, 
                             netmet.scaled),
                          lm(log.bb.abund ~ elev.mean, 
                             netmet.scaled))
summary(mod_niche.overlap)
plot(mod_niche.overlap)
```

@@

@@
